A fast and memory-efficient transition state search method for complex energy landscapes

### 2022-05-18 manuscript.tex
Updated citation information

In each iteration of the string method, each image is evolved downhill for a number of LBFGS iterations before redistributing the images along a cubic-spline interpolated path.
This number of iterations is varied to obtain the fastest convergence, for which we find 2, 50, and 20 to be optimal for the particle cluster, cylidrical buckling, and striped wetting examples, respectively.

@@

\bibitem{Wales2012}
\bibinfo{author}{Wales, D.~J.}
\newblock \bibinfo{title}{{Decoding the energy landscape: Extracting structure,
  dynamics and thermodynamics}}.
\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
  Society A: Mathematical, Physical and Engineering Sciences}}
  \textbf{\bibinfo{volume}{370}}, \bibinfo{pages}{2877--2899}
  (\bibinfo{year}{2012}).

@@

\bibitem{Othayoth2020}
\bibinfo{author}{Othayoth, R.}, \bibinfo{author}{Thoms, G.} \&
  \bibinfo{author}{Li, C.}
\newblock \bibinfo{title}{{An energy landscape approach to locomotor
  transitions in complex 3D terrain}}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{117}}, \bibinfo{pages}{14987--14995}
  (\bibinfo{year}{2020}).

@@

\bibitem{Chi2022}
\bibinfo{author}{Chi, Y.} \emph{et~al.}
\newblock \bibinfo{title}{{Bistable and Multistable Actuators for Soft Robots:
  Structures, Materials, and Functionalities}}.
\newblock \emph{\bibinfo{journal}{Advanced Materials}}  (\bibinfo{year}{2022}).

@@

\bibitem{Shalf2020}
\bibinfo{author}{Shalf, J.}
\newblock \bibinfo{title}{{The future of computing beyond Moore's Law}}.
\newblock \emph{\bibinfo{journal}{Philosophical Transactions Royal Society}}
  \textbf{\bibinfo{volume}{378}}, \bibinfo{pages}{20190061}
  (\bibinfo{year}{2020}).

>>>>

In each iteration of the string method, each image is evolved downhill for a number of L-BFGS iterations before redistributing the images along a cubic-spline interpolated path.
This number of iterations is varied to obtain the fastest convergence, for which we find 2, 50, and 20 to be optimal for the particle cluster, cylidrical buckling, and striped wetting examples, respectively.

@@

\bibitem{Wales2012}
\bibinfo{author}{Wales, D.~J.}
\newblock \bibinfo{title}{{Decoding the energy landscape: Extracting structure,
  dynamics and thermodynamics}}.
\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
  Society A}} \textbf{\bibinfo{volume}{370}}, \bibinfo{pages}{2877--2899}
  (\bibinfo{year}{2012}).

@@

\bibitem{Othayoth2020}
\bibinfo{author}{Othayoth, R.}, \bibinfo{author}{Thoms, G.} \&
  \bibinfo{author}{Li, C.}
\newblock \bibinfo{title}{{An energy landscape approach to locomotor
  transitions in complex 3D terrain}}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences of the United States of America}} \textbf{\bibinfo{volume}{117}},
  \bibinfo{pages}{14987--14995} (\bibinfo{year}{2020}).

@@

\bibitem{Chi2022}
\bibinfo{author}{Chi, Y.} \emph{et~al.}
\newblock \bibinfo{title}{{Bistable and Multistable Actuators for Soft Robots:
  Structures, Materials, and Functionalities}}.
\newblock \emph{\bibinfo{journal}{Advanced Materials}}
  \textbf{\bibinfo{volume}{34}}, \bibinfo{pages}{2110384}
  (\bibinfo{year}{2022}).

@@

\bibitem{Shalf2020}
\bibinfo{author}{Shalf, J.}
\newblock \bibinfo{title}{{The future of computing beyond Moore's Law}}.
\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
  Society A}} \textbf{\bibinfo{volume}{378}}, \bibinfo{pages}{20190061}
  (\bibinfo{year}{2020}).
